### 2025-03-13 paper/quarto_ecml/paper.tex
Fix references

We run the experiments with three gradient-based generators:
\emph{Generic} of \cite{wachter2017counterfactual} as a simple baseline
approach, \emph{REVISE} \cite{joshi2019realistic} that aims to generate
plausible counterfactuals using a surrogate Variational Autoencoder
(VAE), and \emph{ECCo}---the generator of \cite{altmeyer2023faithful}
but without the conformal prediction component---as a method that
directly targets both faithfulness and plausibility of the CEs.

@@

\textbf{\emph{CT is subject to training instabilities.}} Joint
energy-based models are susceptible to instabilities during training
\cite{grathwohl2020your} and even though we depart from the SGLD-based
sampling, we still encounter major variability in the outcomes. CT is
exposed to two potential sources of instabilities: (1) the energy-based
contrastive divergence term in Equation~\ref{eq-div}, and (2) the
underlying counterfactual explainers. For example,
\cite{altmeyer2023faithful} recognize this to be a challenge for
\emph{ECCCo} and so it may have downstream impacts on our proposed
method. Still, we find that training instabilities can be successfully
mitigated by regularizing energy (\(\lambda_{\text{reg}}\)), generating
a sufficiently large number of counterfactuals during each training
epoch, and including only mature counterfactuals for contrastive
divergence.

>>>>

We run the experiments with three gradient-based generators:
\emph{Generic} of \cite{wachter2017counterfactual} as a simple baseline
approach, \emph{REVISE} \cite{joshi2019realistic} that aims to generate
plausible counterfactuals using a surrogate Variational Autoencoder
(VAE), and \emph{ECCo}---the generator of \cite{altmeyer2024faithful}
but without the conformal prediction component---as a method that
directly targets both faithfulness and plausibility of the CEs.

@@

\textbf{\emph{CT is subject to training instabilities.}} Joint
energy-based models are susceptible to instabilities during training
\cite{grathwohl2020your} and even though we depart from the SGLD-based
sampling, we still encounter major variability in the outcomes. CT is
exposed to two potential sources of instabilities: (1) the energy-based
contrastive divergence term in Equation~\ref{eq-div}, and (2) the
underlying counterfactual explainers. For example,
\cite{altmeyer2024faithful} recognize this to be a challenge for
\emph{ECCCo} and so it may have downstream impacts on our proposed
method. Still, we find that training instabilities can be successfully
mitigated by regularizing energy (\(\lambda_{\text{reg}}\)), generating
a sufficiently large number of counterfactuals during each training
epoch, and including only mature counterfactuals for contrastive
divergence.

### 2025-03-13 paper/sections/experiments.qmd
Fix references

We run the experiments with three gradient-based generators: *Generic* of @wachter2017counterfactual as a simple baseline approach, *REVISE* [@joshi2019realistic] that aims to generate plausible counterfactuals using a surrogate Variational Autoencoder (VAE), and *ECCo*---the generator of @altmeyer2023faithful but without the conformal prediction component---as a method that directly targets both faithfulness and plausibility of the CEs.

>>>>

We run the experiments with three gradient-based generators: *Generic* of @wachter2017counterfactual as a simple baseline approach, *REVISE* [@joshi2019realistic] that aims to generate plausible counterfactuals using a surrogate Variational Autoencoder (VAE), and *ECCo*---the generator of @altmeyer2024faithful but without the conformal prediction component---as a method that directly targets both faithfulness and plausibility of the CEs.
